\section{Introduction}
  \paragraph{}
    As smartphones and tablets sales continue to rise enormously nowadays, the need for new mobile applications has obviously not ceased increasing. Developpers have achieved a huge progress in this fieled in the last decade, and still, there are many new and interesting ideas that need to be implemented in the near future.
  \paragraph{}
    Today, mobile applications are covering different palettes of services. Ranging from worldwide daily news, gaming and other entertainment services to social networking and educational services, and from sports, music, and financial services to lifestyle and many other categories.
   \paragraph{}
    Amongst these categories, photo and video applications are increasingly used these days. They allow their users to take pictures, record videos, and share them with their friends. SnapChat is a famous example of these, where the user takes an ephemeral or temporal pictures which will be sent to his/her friends. When the other user receives the pictures, he/she will be able to see it for only few seconds and then the image is completely removed.
    \paragraph{}
    However, if someone reads the SnapChat Terms of Service Licence, which unfortunately the majority of users do not, he/she will notice a major deceptive side of this kind of application:
    \paragraph{}
    \textbf{\textit{\enquote{For all Services[...], you grant Snapchat a worldwide, royalty-free, sublicensable, and transferable license to host, store, use, display, reproduce, modify, adapt, edit, publish, and distribute the content.}}}
    \paragraph{}
    As the above infers, when the user sends a picture to another one, this picture will be stored by the application's server on a specific database and will not be secure. This is a major problem, especially when people are sharing personal and intimate images.
    \paragraph{}
    In this project, we developped a mobile application for both mobile oprating systems: Android and IOS, in which we resolved the problem by using strong cryptographic primitives to provide data confidentiality and integrity during the whole exchange process. This solution provides secure communications between the clients and the server in order to securely exchange session keys which are used then to encrypt images shared between different clients of the application.
    \paragraph{}
    The paper will be organized as follows: in the third section, we will discuss some previous and related works on this subject. In the fourth section, we will present our threat model in which we will discuss some potential threats on the application. Section five will cover a brief overview on the cryptographic primitives and methods used during the developpement. Section six introduces our proposed architecture and how the application works. Finally, section seven will cover the three main implementations: Android, IOS, and the Server side.  